Draft_Figures

### 2018-12-10 draft_figures.Rmd
mpa graph

>>>>

```
##5.	For MPA filter only for those that are “All” for No Take
a.	Total area for each country
b.	Top ten countries by area
i.	make a bar graph and each x-axis label is a country

PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).

MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).

mpa_updated <- read_csv("data/mpa_updated.csv")

mpa <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All") %>%
  group_by(Country)

mpa_area <- aggregate(mpa$REP_M_AREA, by=list(Country=mpa$Country), FUN=sum)
mpa_area

names(mpa_area) <-c("Country", "Area")

mpa_area_10 <- top_n(mpa_area, 10, Area)
mpa_area_10

ggplot(mpa_area_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")

mpa_area_nojurisdiction <-filter(mpa_area, Country != "Areas Beyond National Jurisdiction")
mpa_area_nojurisdiction_10 <- top_n(mpa_area_nojurisdiction, 10, Area)
mpa_area_nojurisdiction_10

ggplot(mpa_area_nojurisdiction_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")
